A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-09-15 src/paper.tex
WIP: Background

Given the limitations of the conventional RC, a novel second screen architecture to identify viewers who are interacting with iTV applications and services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as second screen devices with the aim of capturing personal and contextualized interactions from active viewers in iTV environments. As a result, viewers that interact with an iTV terminal can be properly identified while using a second screen device, which enables to precisely capture their interactions.

An important application... By using proper machine learning algorithms, the personal and contextualized data can reveal important information about viewers' tastes~\cite{Kim2012,Shin2009}.

As an example, the CPs can obtain the user ratings given to TV programs, amount of viewers and user profiles. By using proper machine learning algorithms, CPs can infer viewer tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions is still a challenging activity in the traditional TV environment, which consists of the TV and viewers interacting through a remote control (RC).

% In this research field, a typical approach is to use personal devices (e.g., smartphones and tablets) as secondary screens~\cite{Courtois2012}, since they are almost ubiquitous and present good graphical capabilities. The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users. With respect to interaction capture, an approach described in~\cite{Teixeira2010} shown an architecture to capture contextualized viewers interactions through a conventional RC. In this paper, we present an architecture that facilitates the identification of viewers, which is useful to contextualize the interactions. In addition, the identification of viewers facilitates the capture of their individual interactions.

Since personal devices are almost ubiquitous, they stand out as a powerful mechanism to identify viewers by means of wireless communication technologies~\cite{Cabarcos2011}. In the architecture described in this paper, personal devices play an additional role as a medium of interaction since they are easy and intuitive to use in iTV environments, as pointed out in~\cite{Courtois2012}. An approach described in~\cite{Teixeira2010} has shown an architecture to capture viewers' interactions through a conventional RC. The architecture described in this paper goes further and captures individual and contextualized data. Since the TV environment is shared, the data about nearby viewers is captured to contextualize the interaction with the purpose of helping to infer the behaviors of one viewer toward others ones.

The sections of this paper are arranged as follows: \ldots

\section{Background}

@@

Nowadays, TV viewers rarely just sit passively and watch TV. In many situations, they use second screen devices to perform activities related to TV watching. In the context of TV, second screen refers to the use of a computing device, which is usually a smartphone or a tablet PC, to enhance the viewing experience.

Research studies on second screen have been conducted in TV environments since late 1990s. In 1996, Robertson~\emph{et~al}.~\cite{Robertson1996} developed a prototype where handheld devices were used to control TV and to provide additional content (e.g., textual information) related to the audio-visual content presented in the TV screen. More recent studies show that viewers evaluated positively the use of second screen devices to control the TV and to enrich the TV content~\cite{Cesar2008,Cesar2011,Tsekleves2011}. Cesar~\emph{et~al.}~\cite{Cesar2009} contributed identifying and modeling the requirements to implement an interactive TV architecture based on second screen devices.

@@

\section{Overview of the Second Screen Architecture}

@@

\section{Second Screen Architecture}

@@

\section{Implementation of the Second Screen Architecture}

@@

\section{Experiment: Evaluation of TV Programs using Second Screen}

@@

\section{Conclusions}

>>>>

Given the limitations of the conventional RC, a novel second screen architecture to identify viewers who are interacting with iTV applications and services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as second screen devices with the aim of capturing personal and contextualized interactions from viewers in an iTV environment. Furthermore, the usage of second screen devices offers other advantage. It opens up possibilities to provide viewers with extra information without disturbing the collective experience. For example, each viewer can independently browse through different information about programs and actors in their own devices. As a result, viewers that interact with an iTV terminal by using a second screen device can be properly identified, which enables to precisely capture their interactions.

To illustrate the second screen architecture described in this paper, it was developed a scenario where viewers can use a second screen device to evaluate TV programs. In this scenario, it is possible to browse through TV programs and view extra information about a programs of interest. Viewers' interactions are captured during the use of the second screen device and the data is sent to a remote web application. The applications that were developed in this scenario were tested in commercial platforms that are commonly used by developers and manufacturers as a production environment for both free and paid applications.

Important applications for the data generated during the viewers' interactions with second screen devices are in the field of content personalization. By using proper machine learning algorithms, the data can reveal important information about viewers tastes~\cite{Kim2012,Shin2009}. As a result, CPs can deliver to the right viewer at the right time the right content, which can include targeted advertising, and content recommendation ~\cite{DosSantos2013}.

% The contribution of this paper focuses on the consumption stage, and not so much on the different algorithms for content recommendation ... // Do not focus on content unrelated activity.

The rest of this paper is organized as follows: first, Section~\ref{sec_background} presents a background of the concepts related to the proposed architecture. In Section~\ref{sec_overview} an overview of the proposed architecture is described. Section~\ref{sec_architecture} presents the architecture to capture interactions data from viewers, and Section~\ref{sec_implementation} describes how the architecture was implemented. Finally, Section~\ref{sec_experiment} contains 	an implementation scenario, and Section~\ref{sec_conclusions} provides the conclusions of this work.

\section{Background}
\label{sec_background}

% The connectivity capabilities of smartphones were used in~\cite{Cabarcos2011}, where the Bluetooth technology was used to detect nearby users. With respect to interaction capture, an approach described in~\cite{Teixeira2010} shown an architecture to capture contextualized viewers interactions through a conventional RC. In this paper, we present an architecture that facilitates the identification of viewers, which is useful to contextualize the interactions. In addition, the identification of viewers facilitates the capture of their individual interactions.

% Since personal devices are almost ubiquitous, they stand out as a powerful mechanism to identify viewers by means of wireless communication technologies~\cite{Cabarcos2011}. In the architecture described in this paper, personal devices play an additional role as a medium of interaction since they are easy and intuitive to use in iTV environments, as pointed out in~\cite{Courtois2012}. An approach described in~\cite{Teixeira2010} has shown an architecture to capture viewers' interactions through a conventional RC. The architecture described in this paper goes further and captures individual and contextualized data. Since the TV environment is shared, the data about nearby viewers is captured to contextualize the interaction with the purpose of helping to infer the behaviors of one viewer toward others ones.

@@

Nowadays, TV viewers rarely just sit passively and watch TV. In many situations, they use second screen devices to perform activities related to TV watching. In the context of TV, second screen refers to the use of a computing device as an extended remote control in order to enhance the viewing experience~\cite{Cesar2009}. A typical approach is to use personal devices (e.g., smartphones and tablet PCs) as second screens, since they are almost ubiquitous and present good graphical capabilities~\cite{Courtois2012}.

Research studies on second screen have been conducted in TV environments since late 1990s. In 1996, Robertson~\emph{et~al}.~\cite{Robertson1996} developed a prototype where handheld devices were used to control TV and to provide additional content (e.g., textual information) related to the audio-visual content presented on TV screen. The handheld device can be used both as a stand-alone service and in conjunction with TV. In the latest case, the TV only responds to handheld commands and presents audio-visual content.

More recent studies show that viewers evaluated positively the use of second screen devices to control and to enrich the TV content~\cite{Cesar2008,Cesar2011,Tsekleves2011}. Cesar~\emph{et~al.}~\cite{Cesar2009} contributed identifying and modeling the requirements to implement an iTV architecture based on second screen devices. Through business analysis

an working implementation of this architecture, the authors were able to conclude that second screen devices are considered as a value-added service

@@

\section{Overview of the Second Screen Architecture}
\label{sec_overview}

@@

\section{Architecture to Capture Viewers' Interactions}
\label{sec_architecture}

@@

\section{Implementation of the Second Screen Architecture}
\label{sec_implementation}

@@

\section{Experiment: Evaluation of TV Programs using Second Screen}
\label{sec_experiment}

@@

\section{Conclusions}
\label{sec_conclusions}
